Robust Energy-Aware Routing with Uncertain Traffic Demands

### 2015-01-19 paper.tex
draft for introduction

@@

In this paper, we propose a different approach that finds one energy-aware routing robust to a set of traffic 
matrices, particularly to arbitrary traffic demands. Such a routing without energy consideration is known as 
the demand-oblivious routing, and is well studied\cite{networking:oblivious}. However, the problem becomes much more challenging when energy 
conservation is involved. To overcome the challenges, we first define a new metric, namely oblivious performance 
ratio (OPR) with energy constraint, which reflects the MLUR distance from a routing to the optimal routing when 
certain energy conservation requirement is satisfied. We model the problem of minimizing the performance ratio, 
and analyze the lower and the upper bounds. Then, we propose Robust Energy-Aware Routing (REAR) to solve 
the problem in two phases. REAR select sleeping links based on extended robust link utilization or algebraic 
connectivity, and compute the routing based on a classical demand-oblivious routing algorithm. 
We evaluate our algorithms on real and synthetic topologies. The simulation results show that REAR can save 
19\% of line card power while the performance ratio is less than 34\%.
\end{abstract}

@@

\section{Introduction}
We aim to find the ``robust'' route for all possible traffic matrix, not only consider performance but also energy 
consumption in network.

\section{Motivation}
Suppose two hosts named host A and host B, and there are three links between 
them, respectively, capacity with 2M, 3M and 5M. Now demands come, with 1M from A to B. we regard the capacity 
as the power of the link, and the minimum maximum utilization of network links as a metric of the network performance. 
There are two directions for operating this example. One consider the min power consumption except for the 
utilization, it is obviously that we should close the larger power consuming links, such as the 5M and 3M links, and 
all the traffic go through the 2M link. In this way, the min max utilization of network is 0.5 and the power consuming 
is 2 units (means the power difference come from the link mainly). The other consider the power except for the 
utilization reversely, so we should split the 1M traffic to three parts, 0.2M across 2M link, 0.3M across 3M link and 
0.5M across 5M, consequently with a min max utilization of 0.1, but the power is 10 units however.

Two directions mentioned above both are extremely single-consideration. Previous researchers solve the problem more 
considerable, include ``GreenTE'' and ``a\%-green is engouh''. The former set a threshold of min max utilization, 
close links as many as possible to achive the most power saving. And the latter one set a destination of the power 
saving, calculate optimal route for get the min max utilization. Two work have their restriction, which both need a 
specific traffic matrix that as base of their optimization.

But the need of precise current traffic matrix shound be carefully checked. Although some researcher contribute to this 
area, the real precise traffic matrix still be a challenge. Take a step back, the dynamic of traffic matrix is more 
diffcult even if we obtain the precise current one. Futhermore, ISP will not want to change their route policy 
frequently, as it will result in other route failure possiblly. So our question is that : Is there exist a route both 
satisfy power and utilization requirement for any traffic matrix given?

David Applegate propose a method for obtain a route wihich is ``robust'' to variations in demands for a specific network topology.

@@

\section{Related Work}
related work.

>>>>

\makeatletter
\newcommand{\rmnum}[1]{\romannumeral #1}
\newcommand{\Rmnum}[1]{\expandafter\@slowromancap\romannumeral #1@}
\makeatother

@@

In this paper, we propose a different approach that finds one energy-aware routing robust to a set of traffic 
matrices, particularly to arbitrary traffic demands. Such a routing without energy consideration is known as 
the demand-oblivious routing, and is well studied. However, the problem becomes much more challenging when energy 
conservation is involved. To overcome the challenges, we first define a new metric, namely oblivious performance 
ratio (OPR) with energy constraint, which reflects the MLUR distance from a routing to the optimal routing when 
certain energy conservation requirement is satisfied. We model the problem of minimizing the performance ratio, 
and analyze the lower and the upper bounds. Then, we propose Robust Energy-Aware Routing (REAR) to solve 
the problem in two phases. REAR select sleeping links based on extended robust link utilization or algebraic 
connectivity, and compute the routing based on a classical demand-oblivious routing algorithm. 
We evaluate our algorithms on real and synthetic topologies. The simulation results show that REAR can save 
19\% of line card power while the performance ratio is less than 34\%.
\end{abstract}

@@

\section{Introduction}
Internet was playing a more and more important role in our daily life, as an huge and indispensable communication system
it also has its considerable share in energy consumption. Devices such as routers and switchs contributed to the most
consumption because of inefficient energy management solutions, which made the devices always working in full mode 
regardless of traffic demands. In particular, even there are no traffic in the link between two routers or switches, 
the line cards related to the link were still working and in previous research line cards are the main energy consuming part of
routers or switches. So for energy consideration, we should obtain link-level solutions which switched the link (line cards)
to sleep mode if there is no traffic on it.

Usually, We computed routing to stipulate how is the traffic going, aimed to achieved some traffic engineering goals such as 
the maximum link utilization ratio (MLUR). In details, we used traffic demands and network topology as input for routing 
computation process, then combined routing and traffic demands to get the traffic on each link, based on which we determind
which link can be put to sleep. However, measuring and predicting accurate traffic demands are difficult, so did the dynamic
natrue. Even getting all knowledge about traffic demands, the related routing shift frequently when the traffic demands
changes. It means that we should change the link (line cards) working mode frequently according to routing, and it is 
unpractical. So the robust routing is needed, which based on the approximate traffic demands and was robust to sudden traffic changes.
Such a routing is known as the demand-oblivious routing and is well studied in \cite{networking:oblivious}, which proposed
the algorithm for computing robust routing with uncertain traffic demands on specific topology.

Unfortunately, there is no metric in such robust routing to measure the importance of links, in another word, we have no 
ideas to put which link to sleep mode. Furthermore, when some links are switched off and the topology changed actually, but we 
still have no ideas on how to adjust the routing in final topology. Another challenge is that, to achieve the power saving
goals we may should switch off not only one link, and it is a classical NP-Hard problem. To overcome the challenges,
we define a metric namely extended robust link utilization (ERLU) to measure the traffic engineering natrue without real traffic 
demands, and define oblivious performance ratio (OPR) to reflect the MLUR distance from a routing to the optimal
when certain energy conservation requirement is satisfied. We use algebraic connectivity \cite{networking:algebraic} and 
ERLU as criterion to switch off links, and use OPR to adjust routing.

Our main contribution in this paper contains three aspects. Firstly, we model the problem of minimizing the OPR, then
analyze the lower and the upper bounds. Secondly, we proposed an heuristic algorithm named Robust Energy-Aware Routing (REAR) 
to solve the problem in two phases, included choosing links to sleep and adjust routing. Thirdly, we implemented our
algorithm in real topology and arbitrary traffic demands to observe the relationship between power saving and OPR. The
simulation results show that REAR can save 19\% of line card power while OPR is less than 34\% in some topology. Also 
we investigate the path stretching problem.

The rest of the paper is organized as follows. Section \Rmnum{2} reviews the related work and Section \Rmnum{3}
define two new metric and model our problem. Following we proposed our algorithm in Section \Rmnum{4}. For understanding
more clear on our problem, we give two simple samples and prove the bounds in Section \Rmnum{5}. Experiments are discribed
and result are showed in Section \Rmnum{6}. We discuss issues and future work in Section \Rmnum{7}, then conclude in 
Section \Rmnum{8}

\section{Related Work}
related work

@@

\section{Future and Issue}
Future and Issue
